A Computational Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-02 paper/paper.tex
pass over biology half

\subsection{Sketch of our main contributions}
We argue that the implication of the DMN in a
diversity of humans' most advanced cognitive processes
can be parsimoniously recast as prediction error minimization
based on pervasive probabilistic simulations,
thus maximizing reward outcome at various time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo sampling
\citep{tenenbaum2011grow}.
\textit{Control} refers to the influences that an agent exerts when interacting
with the environment to encourage preferred states.
Even (necessarily imperfect) memories
of past experience, random mind-wandering and dreams during sleep
may provide meaningful building blocks to iteratively improve
the predictive DMN machinery to optimize the behavior of the organism.
%
In short, it has been proposed earlier that
the human brain's energy budget is largely dedicated to
``the development and maintenance of [a]
probabilistic model of anticipated events''
\citep{raichle2005intrinsic}.
The idea has been invigorated by empirical evidence from
neuroscientific experiments \citep{kording2004bayesian, fiser2004small}.
This paper proposes a formal model that satisfies this contention.

\section{Known Neurobiological Properties of the Default Mode Network}
We begin by a deconstruction the overall DMN function
by the mechanistic relevance of each individual network node
based on published findings from neuroscience experiments.
%
\subsection{The posteromedial cortex: Global monitoring and integration}
Among all parts of the human brain,
the midline structures of the DMN,
including the posteromedial cortex (PMC) and
the medial prefrontal cortex (mPFC),
are responsible for the highest metabolic turn-over
of glucose energy consumption \citep{raichle2001pnas}.
These metabolic characteristics go hand-in-hand with
brain-imaging analyses \citep{andrews2010} in
suggesting that the PMC and dmPFC
potentially represent the functional backbone of the DMN.

The PMC myelinates relatively late during postnatal development in monkeys
\citep{goldman1987development}, generally considered to
be a sign of phylogenetic sophistication \citep{flechsig1920}.
Physiological and disturbed metabolic fluctuations in the
human PMC have been repeatedly related to
phenomena of changed conscious awareness \citep{cavanna2006precuneus},
including anesthesia, sleep, and coma.
%
Indeed,
the PMC has long been speculated to reflect constant computation of
the environmental statistics and its internal representation
as an "inner minds eye" \citep{cavanna2006precuneus, leech_pcc2014}.
For instance, B\'alint's syndrome is a neurological disorder of conscious
awareness that results from damage in the bilateral parietal cortex
\citep{balint1909seelenlahmung}.
Patients are plagued by an
inability to bind various individual features of the visual
environment into an integrated whole (i.e., simultanagnosia)
as well as inability to direct action towards
currently unattended environmental objects
(i.e., optic ataxia).
This can be viewed as a high-level impairment in the gathering
of information about alternative objects (i.e., exploration) as well as
leveraging these environmental opportunities (i.e., exploitation).
Congruently,
the human PMC was coupled in two functional connectivity modalities
with the amygdala involved in significance evaluation and
the nucleus accumbens (NAc), involved in reward evaluation.
Specifically, among all parts of the PMC,
the human ventral posterior cingulate cortex was
most connected to the laterobasal
nuclei group of the amygdala
\citep{bzdok2015subspecialization}.
This amygdalar subregion has been proposed to
continuously scan environmental input
for biological significance assessment.

This putative role of the PMC in continuous integration of environmental relevance
and ensuing top-level control of action in the environment is supported
by a number of neuroscience experiments.
Electrophysiological recordings in animals implicated the PMC in
strategic decision making \citep{pearson2009neurons},
risk assessment \citep{mccoy2005risk},
and outcome-contingent behavioral modulation \citep{hayden2009electrophysiological},
while its retrosplenial portion was
more specifically implicated in approach-avoidance behavior
\citep{vann2009does}.
Neuron spiking activity in the PMC allowed distinguishing
whether a monkey would persue an exploratory or exploitative
behavioral strategy in a complex food foraging task \citep{pearson2009neurons}.
Further, single-cell recordings in the monkey PMC
demonstrated this brain region's sensitivity to
subjective target utility \citep{mccoy2005risk} and integration
across individual decision-making instances \citep{pearson2009neurons}.
This DMN node encoded the
preference of or aversion to options with uncertain reward outcomes
and its spiking activity was more associated with
subjectively perceived relevance of a chosen object
than by its factual value, based on an internal currency of value.
In fact, direct stimulation of PMC neurons
promoted exploratory action towards options
with unsafe reward outcomes that were previously shunned.
Graded changes in firing rates of PMC neurons
indicated changing choices in upcoming trials and their neural patterns were
distinct from spike firings that indicated choosing either option.
Similarly in humans,
the DMN has been shown to gather and integrate information
over different paragraphs in an fMRI study on auditory narratives
\citep{simony2016dynamic}.
%
The retrosplenial portion of the PMC can subserve action possibilities
and evaluation of reward contingencies by integrating these with
information from memory and altered perspective frames.
Regarding memory retrieval, retrosplenial lesions have been
consistently associated with anterograde and retrograde memory impairments
of various kinds of sensory information
in rabbits and humans
\citep{vann2009does}.
Regarding perspective frames, this PMC subregion has been
proposed to mediate between the organism's egocentric
(i.e., focused on sensory input) and
allocentric (i.e., focused on world knowledge) viewpoints
in animals and humans
\citep{epstein2008parahippocampal, burgess2008spatial, valiquette2007different}.

Consequently, the PMC may monitor the subjective outcomes
of possible decisions and integrates that information
with memory, perspective frames, and
reward schedules into higher-level strategies.
Perceived value that differs across individuals updates
statistical assessment of the environment
to predict delayed reward opportunities in the future.
In doing so, the PMC continuously adapts to changes
in both the external environment and its internal representation
that modulate strategic behavioral adjustment in volatile environments.

\subsection{The prefrontal cortex: Stimulus-value association and action consideration}
Analogous to the PMC,
the dorsomedial PFC (dmPFC) is believed to subserve predominantly ambiguous processes
across time, space, and content domains in
sensory-independent top-down pathways.
In contrast to the PMC, however,
the dmPFC may be the DMN node whose function comes closest to a “mental sketchpad”
\citep{goldman1996prefrontal}, as it 
potentially subserves the de-novo generation and binding
of meaning representations instructed by stored semantics and memories.

Generally,
patients with neurological lesions in the prefrontal cortex
are known to adapt to novel situations and stimuli with difficulty
\citep{stuss1986frontal}.
The dmPFC may subserve inference, representation, and assessment
of one's own and other individuals' action considerations.
Specifically, neural activity in human dmPFC
reflected expectations about other peoples actions and errors thereof.
dmPFC activity indeed explained the proficiency decline
of inferring other peoples' thoughts in the elderly \citep{moran2012social}.
Some dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances \citep{yoshida2010neural}.
In fact, the topographically neighboring dorsal anterior cingulate cortex
has also been linked to computing values and efforts of
persisting a behavioral plan versus switching the
environmental context in several lesion studies \citep{kolling2016value}.
%
Such highly abstract neural computations necessarily rely on the
generation of probabilistic internal information drawing from
episodic memory retrieval, generative construction processes,
and explicit knowledge of the external world.
%
According to computational neuroimaging experiments,
the dmPFC activity preferentially models stimulus-value associations of
possible actions that are not actually executed,
whereas the vmPFC activity models value in the environment that leads performed actions
\citep{nicolle2012agent}.

In contrast to the dorsomedial prefrontal DMN,
the ventromedial portion of the prefrontal cortex (vmPFC) probably subserves
less ambiguous subjective-value-related evaluative processes and
reward-informed risk estimation of self-relevant environmental stimuli.
This DMN node is more closely associated with
orchestrating adapted behavior by bottom-up-driven
processing of “what matters now”,
probably drawing on model-based value representations
\citep{doherty2015structure}.
Quantative lesion findings across 344 human individuals confirmed
a gross impairment in value-based decision making
\citep{glascher2012lesion}.
Indeed,
the vmPFC is preferentially connected with limbic and reward-related areas.
The vmPFC has been observed to have monosynaptical connections
with the NAc
in axonal tracing studies in monkeys \citep{haber1995orbital}.
Additionally, the gray-matter volume of the vmPFC and NAc
correlated with indices of value-guided behavior and reward attitudes
\citep{lebreton2009automatic}.
NAc activity is thought to reflect reward prediction signals from dopaminergic pathways
\citep{schultz1998predictive}
that not only modulate motivated behavior towards basic survival needs but also
subserve RL in humans more broadly \citep{doherty2015structure}.
This is consistent with diffusion MRI (dMRI) tractography in humans and monkeys
\citep{croxson2005quantitative} that
quantified this brain regions to
be substantially more likely connected to the vmPFC than dmPFC in both species.
Two functional connectivity modalities in humans strongly connected
the vmPFC with the NAc, hippocampus (HC),
and posteromedial cortex.
%
The vmPFC is often proposed to be involved in (external) emotional
reactions and own (visceral) arousal.
Real or imaginged bodily states could be mapped in the vmPFC
as a bioregulatory disposition governing cognition
and decision making \citep{damasio1996somatic}
In neuroeconomic studies of human decision making,
the vmPFC consistently reflects an individual’s subjective
valuation
\citep{behrens2008associative}.
This may be why performance within and across participants
was related to state encoding in vmPFC.
Such a \textit{cognitive map} of action space was argued to encode
the current task state even when states are unobservable from sensory input,
which was shown to be critical for behavior \citep{Schuck2016}.
Additionally,
independent whole-brain analyses from structural
neuroimaging studies related the gray-matter volume GMV of the vmPFC,
more consistently than any other
brain region, to indices of
social competence and social network complexity,
among the most complicated decision that humans and monkeys take
\citep{behrens2009computation}.
%

\subsection{The hippocampus: Memory, space, and experience replay}
The core structures of the DMN midline are probably in constant communication
with the HC in the medial temporal lobe \citep{vincet2006}.
The HC is well known to be involved in memory and spatial navigation in animals and humans.

Its highly recursive anatomical architecture
may be specifically designed to allow reconstructing
entire episodes of experience from memory fragments.
%
While the HC
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general
\citep{maguire2016, schacter2007remembering, gelbard2008internally, Javadi2017}.
Indeed,
hippocampal damage is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also thinking about one’s own future and
imagining new fictitious experiences more broadly \citep{hassabis2007patients}.
Mental scenes created by hippocampus-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal hippocampus revealed
some constantly active neuronal ensembles whose firing coincided with
distinct locations in space while the animal navigated through its surroundings.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased grey matter volume in the
posterior hippocampus \citep{maguire2000navigation}.
Indeed, place-specific neuronal populations in the hippocampus
spike one after another when an animal is choosing between alternative
paths \citep{johnson2007neural}; and
these neuronal patterns apear to also indicate upcoming behavior
\citep{pfeiffer2013hippocampal}.

But encoding and generative reconstruction in the hippocampus extends
beyond mere spatial knowledge of the environment.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events \citep{buzsaki2004large}.
Specific spiking sequences, that were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during
quiet wakefulness and sleep \citep{hartley2014space, o2010play}.
Moreover, spike sequences measured in hippocampal place cells of rats
featured reoccurrence directly after experimental trials
as well as directly before upcoming experimental trials \citep{diba2007forward}.
Such hippocampal ensemble burts during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, potentially also in the nodes of the DMN.
These mechanisms of the hippocampus probably make important contributions to the
recollection of autobiographical memory episodes and other
reexperienced or newly generated mental scenarios
\citep{hassabis2007patients}.

@@

The TPJ in the left hemisphere (LTPJ) in turn exhibits a close topographical relationship to Wernicke's area
involved in the comprehension or understanding of written and spoken language.
Neurological patients with damage caused to Wernicke's area
have a major impairment of language comprehension
when listening to others or reading a book.
Their speech
preserves natural rhythm and about normal syntax, yet the
voiced sentences are devoid of meaning (i.e., aphasia).
Abstracting from the typical semantic interpretations in linguistics
and neuropsychology,
the LTPJ probably mediates access to and integrating of world knowlege
to model action concepts
\citep{binder2011neurobiology, seghier2013angular}.
For instance, LTPJ lesions also entail problems in recognizing
others' pantomimed action towards objects
without obvious relation to processing any language content
\citep{varney1987locus}
% (Varney and Damasio 1987; Rothi et al. 1991; Buxbaum et al. 2005).
%
Also inner speech hinges on knowledge retrieval of statistical structure
about the physical and inter-personal world.
Indeed,
the internal production of
formulated thought ("language of the mind") was closely related to the left TPJ
in a multivariate analysis of brain volume
\citep{geva2011neural}.
Further,
episodic memory recall and imagination strongly draw on
complex world knowledge.
Isolated building blocks of world statistics probably get reassembled
in internally generated visual scenarios that
navigate present action, weigh hypothetical possibilities, and forcast the future.
%
The LTPJ may hence facilitate the automated prediction of events
by incorporating experience-derived models of the world
into ongoing action, planning, and problem solving.
% world -> policy matrix driven computation
% self -> value matrix driven computation

@@

\section{Conclusion}
What brain function could be important enough
for the existence and survival of the human species
to warrant constant, high energy costs?
MDPs provide an attractive
process model how the human association cortex
might implement supra-modal representation and control of the environment to
optimize the organism's fate.
% by obtaining reward and avoiding pain.
This idealized process model explains
a number of previous experimental observations in the
DMN by a simple but non-trivial mechanism.
%
From the computational view of a Markovian sequential decision process,
behavior unfolds by integrating happened past events
and possible future events to guide action choice in the present context.
This functional account is more compatible with the DMN's
poorly understood involvement across
autobiographical memory retrieval, problem solving,
abstract reasoning based on internally generated scenes, social cognition,
as well as delay discounting and self-related prospection.
MDPs provide a mathematical formalism how
optimal substructure in the environment can be recursively exploited
when confronted with complicated decisions.
Improvement of the internal world model
by injecting stochasticity in the recall of past
actions and outcomes may explain why
very accurate memories have been disfavored in human evolution
and why human creativity might be adaptive.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of intelligent RL systems.
The proposed machine-learning perspective
on DMN function is hence not only practically computable but
also neuroscientifically falsifiable.
At the least, we propose an alternative vocabulary to
describe and interpret experimental findings in neuroscience studies
on the default mode network.
%
Ultimately,
the DMN can be viewed as a functional integrator
from the relatively recent events to anticipated upcoming events
in order to constantly improve present action in the dynamic world.

>>>>

\subsection{Sketch of our main contributions}
We argue that the implication of the DMN in a
diversity of humans' most advanced cognitive processes
can be parsimoniously recast as prediction error minimization
based on pervasive probabilistic simulations,
thus maximizing reward outcome at various time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo sampling
\citep{tenenbaum2011grow}.
\textit{Control} refers to the influences that an agent exerts when interacting
with the environment to encourage preferred states.
Even (necessarily imperfect) memories
of past experience, random day-time mind-wandering and dreams during sleep
may provide meaningful building blocks to iteratively improve
the predictive DMN machinery to optimize the behavior of the organism.
%
In short, it has been proposed earlier that
the human brain's energy budget is largely dedicated to
``the development and maintenance of [a]
probabilistic model of anticipated events''
\citep{raichle2005intrinsic}.
The idea has been invigorated by empirical evidence from
neuroscientific experiments \citep{kording2004bayesian, fiser2004small}.
This paper proposes a formal model that satisfies this contention.

\section{Known neurobiological properties of the default mode network}
We begin by a deconstruction the overall DMN function
by the mechanistic relevance of each individual network node
based on published findings from neuroscience experiments.
%
\subsection{The posteromedial cortex: Global monitoring and information integration}
Among all parts of the human brain,
the midline structures of the DMN,
including the posteromedial cortex (PMC) and
the medial prefrontal cortex (mPFC),
are responsible for the highest metabolic turn-over
of glucose energy consumption \citep{raichle2001pnas}.
These metabolic characteristics go hand-in-hand with
brain-imaging analyses \citep{andrews2010} in
suggesting that the PMC and dmPFC
potentially represent the functional backbone of the DMN.

The PMC myelinates relatively late during postnatal development in monkeys
\citep{goldman1987development}, which is generally considered to
be a sign of phylogenetic sophistication \citep{flechsig1920}.
Physiological and disturbed metabolic fluctuations in the
human PMC have been repeatedly related to
phenomena of changed conscious awareness \citep{cavanna2006precuneus},
including anesthesia, sleep, and coma.
%
Indeed,
the PMC has long been speculated to reflect constant computation of
the environmental statistics and its internal representation
as an "inner minds eye" \citep{cavanna2006precuneus, leech_pcc2014}.
For instance, B\'alint's syndrome is a neurological disorder of conscious
awareness that results from damage in the bilateral parietal cortex
\citep{balint1909seelenlahmung}.
Patients are plagued by an
inability to bind various individual features of the visual
environment into an integrated whole (i.e., simultanagnosia)
as well as inability to direct action towards
currently unattended environmental objects
(i.e., optic ataxia).
This can be viewed as a high-level impairment in the gathering
of information about alternative objects (i.e., exploration) as well as
leveraging these environmental opportunities (i.e., exploitation).
Congruently,
the human PMC was coupled in two functional connectivity modalities
with the amygdala, involved in significance evaluation, and
the nucleus accumbens (NAc), involved in reward evaluation.
Specifically, among all parts of the PMC,
the human ventral posterior cingulate cortex was
most connected to the laterobasal
nuclei group of the amygdala
\citep{bzdok2015subspecialization}.
This amygdalar subregion has been proposed to
continuously scan environmental input
for biological significance assessment.

The putative role of the PMC in continuous integration of environmental relevance
and ensuing top-level control of action in the environment is supported
by a number of neuroscience experiments.
Electrophysiological recordings in animals implicated the PMC in
strategic decision making \citep{pearson2009neurons},
risk assessment \citep{mccoy2005risk},
and outcome-contingent behavioral modulation \citep{hayden2009electrophysiological},
while its retrosplenial portion was
more specifically implicated in approach-avoidance behavior
\citep{vann2009does}.
Neuron spiking activity in the PMC allowed distinguishing
whether a monkey would persue an exploratory or exploitative
behavioral strategy in a complex food foraging task \citep{pearson2009neurons}.
Further, single-cell recordings in the monkey PMC
demonstrated this brain region's sensitivity to
subjective target utility \citep{mccoy2005risk} and integration
across individual decision-making instances \citep{pearson2009neurons}.
This DMN node encoded the
preference of or aversion to options with uncertain reward outcomes
and its spiking activity was more associated with
subjectively perceived relevance of a chosen object
than by its factual value, based on an internal currency of value.
In fact, direct stimulation of PMC neurons
promoted exploratory action towards options
with unsafe reward outcomes that were previously shunned.
Graded changes in firing rates of PMC neurons
indicated changing choices in upcoming trials and their neural patterns were
distinct from spike firings that indicated choosing either option.
Similarly in humans,
the DMN has been shown to gather and integrate information
over different paragraphs in an fMRI study on auditory narratives
\citep{simony2016dynamic}.
%
The retrosplenial portion of the PMC can subserve action possibilities
and evaluation of reward contingencies by integrating these with
information from memory and different perspective frames.
Regarding memory retrieval, retrosplenial lesions have been
consistently associated with anterograde and retrograde memory impairments
of various kinds of sensory information
in rabbits and humans
\citep{vann2009does}.
Regarding perspective frames, this PMC subregion has been
proposed to mediate between the organism's egocentric
(i.e., focused on sensory input) and
allocentric (i.e., focused on world knowledge) viewpoints
in animals and humans
\citep{epstein2008parahippocampal, burgess2008spatial, valiquette2007different}.

Consequently, the PMC may contribute to overall DMN function
by monitoring the subjective outcomes
of possible decisions and integrates that information
with memory, perspective frames, and
reward schedules into higher-level strategies.
Perceived value that differs across individuals updates
statistical assessment of the environment
to predict delayed reward opportunities in the future.
In doing so, the PMC continuously adapts to changes
in both the external environment and its internal representation
that modulate strategic behavioral adjustment in volatile environments.

\subsection{The prefrontal cortex: Stimulus-value association and action consideration}
Analogous to the PMC,
the dorsomedial PFC (dmPFC) is believed to subserve predominantly ambiguous processes
across time, space, and content domains in
sensory-independent top-down pathways.
In contrast to the PMC, however,
the dmPFC may be the DMN node whose function comes closest to a
``mental sketchpad'' \citep{goldman1996prefrontal}, as it 
potentially subserves the de-novo generation and binding
of meaning representations instructed by stored semantics and memories.

Generally,
patients with neurological lesions in the prefrontal cortex
are known to adapt to novel situations and stimuli with difficulty
\citep{stuss1986frontal}.
The dmPFC may subserve inference, representation, and assessment
of one's own and other individuals' action considerations.
Specifically, neural activity in the human dmPFC
reflected expectations about other peoples actions and errors thereof.
dmPFC activity indeed explained the proficiency decline
of inferring other peoples' thoughts in the elderly \citep{moran2012social}.
Some dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances \citep{yoshida2010neural}.
In fact, the topographically neighboring dorsal anterior cingulate cortex
has also been linked to computing values and efforts of
persisting a behavioral plan versus switching the
environmental context in several lesion studies \citep{kolling2016value}.
%
Such highly abstract neural computations necessarily rely on the
generation of probabilistic internal information drawing from
episodic memory retrieval, generative construction processes,
and explicit knowledge of the external world.
%
According to computational neuroimaging experiments,
the dmPFC activity preferentially models stimulus-value associations of
possible actions that are not actually executed,
whereas the vmPFC activity models value in the environment that leads performed actions
\citep{nicolle2012agent}.

In contrast to the dorsomedial prefrontal DMN,
the ventromedial portion of the prefrontal cortex (vmPFC) probably subserves
less ambiguous subjective-value-related evaluative processes and
reward-informed risk estimation of self-relevant environmental stimuli.
This DMN node is more closely associated with
orchestrating adaptive behavior by bottom-up-driven
processing of “what matters now”,
probably drawing on model-based value representations
\citep{doherty2015structure}.
Quantative lesion findings across 344 human individuals confirmed
a gross impairment in value-based decision making
\citep{glascher2012lesion}.
Indeed,
the vmPFC is preferentially connected with reward-related and limbic areas.
The vmPFC has been observed to have monosynaptical connections
with the NAc
in axonal tracing studies in monkeys \citep{haber1995orbital}.
Additionally, the gray-matter volume of the vmPFC and NAc
correlated with indices of value-guided behavior and reward attitudes
\citep{lebreton2009automatic}.
NAc activity is thought to reflect reward prediction signals from dopaminergic pathways
\citep{schultz1998predictive}
that not only modulate motivated behavior towards basic survival needs but also
subserve RL in humans more broadly \citep{doherty2015structure}.
This is consistent with diffusion MRI tractography in humans and monkeys
\citep{croxson2005quantitative} that
quantified this brain regions to
be substantially more likely connected to the vmPFC than dmPFC in both species.
Two functional connectivity modalities in humans strongly connected
the vmPFC with the NAc, hippocampus (HC),
and posteromedial cortex.
%
The vmPFC is often proposed to be involved in (external) emotional
reactions and own (visceral) arousal.
Real or imaginged bodily states could be mapped in the vmPFC
as a bioregulatory disposition governing cognition
and decision making \citep{damasio1996somatic}
In neuroeconomic studies of human decision making,
the vmPFC consistently reflects an individual’s subjective
valuation
\citep{behrens2008associative}.
This may be why performance within and across participants
was related to state encoding in vmPFC.
Such a ``cognitive map'' of action space was argued to encode
the current task state even when states are unobservable from sensory input,
which was shown to be critical for behavior \citep{Schuck2016}.
Additionally,
independent whole-brain analyses from structural
neuroimaging studies related the gray-matter volume of the vmPFC,
more consistently than any other
brain region, to indices of
social competence and social network complexity, which are
among the most complicated decision that humans and monkeys take
\citep{behrens2009computation}.
%

\subsection{The hippocampus: Memory, space, and experience replay}
The midline core of the DMN is probably in constant communication
with the HC in the medial temporal lobe \citep{vincet2006}.
The HC is long known to be involved in memory and spatial navigation in animals and humans.

Its highly recursive anatomical architecture
may be specifically designed to allow reconstructing
entire episodes of experience from memory fragments.
%
While the HC
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general
\citep{maguire2016, schacter2007remembering, gelbard2008internally, Javadi2017}.
Indeed,
hippocampal damage is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also thinking about one's own future and
imagining new fictitious experiences more broadly \citep{hassabis2007patients}.
Mental scenes created by hippocampus-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal hippocampus revealed
some constantly active neuronal ensembles whose firing coincided with
distinct locations in space while the animal navigated through its surroundings.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased grey matter volume in the
hippocampus \citep{maguire2000navigation}.
Indeed, place-specific neuronal populations in the hippocampus
spike one after another when an animal is choosing between alternative
paths \citep{johnson2007neural}; and
these neuronal patterns appear to also indicate upcoming behavior
\citep{pfeiffer2013hippocampal}.

But encoding and generative reconstruction in the hippocampus extends
beyond mere spatial knowledge of the environment.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events \citep{buzsaki2004large}.
Specific spiking sequences, that were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during
quiet wakefulness and sleep \citep{hartley2014space, o2010play}.
Moreover, spike sequences measured in hippocampal place cells of rats
featured reoccurrence directly after experimental trials
as well as directly before upcoming experimental trials \citep{diba2007forward}.
Such hippocampal ensemble burts during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, potentially also in the nodes of the DMN.
These hippocampus-subserved mechanisms
probably make important contributions to the
recollection of autobiographical memory episodes and other
reexperienced or newly generated mental scenarios
\citep{hassabis2007patients}.

@@

The TPJ in the left hemisphere (LTPJ) in turn exhibits a close topographical relationship to Wernicke's area
involved in the comprehension or understanding of written and spoken language.
Neurological patients with damage caused to Wernicke's area
have a major impairment of language comprehension
when listening to others or reading a book.
Their speech
preserves natural rhythm and about normal syntax, yet the
voiced sentences are devoid of meaning (i.e., aphasia).
Abstracting from the typical semantic interpretations in linguistics
and neuropsychology,
the LTPJ probably mediates access to and integration of world knowlege
to model action concepts
\citep{binder2011neurobiology, seghier2013angular}.
For instance, LTPJ lesions also entail problems in recognizing
others' pantomimed action towards objects
without obvious relation to processing explicit language content
\citep{varney1987locus}
% (Varney and Damasio 1987; Rothi et al. 1991; Buxbaum et al. 2005).
%
Inner speech also hinges on knowledge retrieval of statistical structure
about the physical and inter-personal world.
Indeed,
the internal production of
formulated thought ("language of the mind") was closely related to the left TPJ
in a multivariate analysis of brain volume
\citep{geva2011neural}.
Further,
episodic memory recall and imagination strongly draw on
complex world knowledge.
Isolated building blocks of world statistics probably get reassembled
in internally generated visual scenarios that
navigate present action, weigh hypothetical possibilities, and forecast the future.
%
The LTPJ may hence facilitate the automated prediction of events
by incorporating experience-derived models of the world
into ongoing action, planning, and problem solving.
% world -> policy matrix driven computation
% self -> value matrix driven computation

@@

\section{Conclusion}
What brain function could be important enough
for the existence and survival of the human species
to warrant constant, high energy costs?
MDPs provide an attractive
process model how the human association cortex
might implement supra-modal representation and control of the environment to
optimize the organism's fate.
% by obtaining reward and avoiding pain.
This idealized process model explains
a number of previous experimental observations in the
DMN by a simple but non-trivial mechanism.
%
From the computational view of a Markovian sequential decision process,
behavior unfolds by integrating happened past events
and possible future events to guide action choice in the present context.
This functional account is more compatible with the DMN's
poorly understood involvement across
autobiographical memory retrieval, problem solving,
abstract reasoning based on internally generated scenes, social cognition,
as well as delay discounting and self-related prospection.
MDPs provide a mathematical formalism how
optimal substructure in the environment can be recursively exploited
when confronted with complicated decisions.
Improvement of the internal world model
by injecting stochasticity in the recall of past
actions and outcomes may explain why
very accurate memories have been disfavored in human evolution
and why human creativity might be adaptive.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of intelligent RL systems.
The proposed machine-learning perspective
on DMN biology is hence not only practically computable but
also neuroscientifically falsifiable.
At the least, we propose an alternative vocabulary to
describe and interpret experimental findings in neuroscience studies
on the DMN.
%
Ultimately,
the DMN can be viewed as a functional integrator
from the relatively recent events to anticipated upcoming events
in order to constantly improve present action in our dynamic world.
